Making Deep Q-learning Methods Robust to Time Discretization

### 2019-01-22 paper/icml_drau/advup.tex

@@

\begin{theorem}
Consider a near-continuous MDP in which an agent selects an
action according to an $\eps$-greedy policy that mixes a deterministic
exploitation policy $\pi$ with an action taken from a noise policy
$\pi^\text{noise}(a|s)$ with probability $\eps$ at each step. Then the
agent's trajectories converge when $\deltat\to 0$ to the solutions of the
\emph{deterministic} equation
\begin{equation}
d s_t/dt= (1-\eps) F(s_t,\pi(s_t))+\eps \E_{a\sim
\pi^\text{noise}(a|s)}F(s_t,a)
\end{equation}
\end{theorem}

@@

$V_{\theta}$ and $A_{\psi}$ are learned by a variants of $Q$-learning for continuous and
discrete action spaces are used. Namely, 
the true $A^\pi_\deltat$
and $V^\pi_\deltat$ of a near-continuous MDP with greedy exploitation
policy $\pi(s) \deq
\text{argmax}_{a'}A^\pi_\deltat(s, a')$
are the unique solution to the Bellman and consistency equations
\begin{align}
	V^{\pi}_\deltat(s) + \deltat\, A^{\pi}_\deltat(s, a) &=
	r\,\deltat + \gamma^{\deltat}  \,\E_{s'} V^{\pi}_\deltat(s')\label{eq:bellman_A}\\
	A^{\pi}_\deltat(s, \pi(s)) &= 0\label{eq:max_A}.
\end{align}
as seen in \ref{subsec:reparam}. Then $V_{\theta}$
and $A_{\psi}$ are trained to approximately solve these equations.

>>>>

\TODO{
\begin{theorem}
Under suitable smoothness assumptions, $A^\pi_\deltat(s,a)$ has a limit
$A^\pi(s,a)$ when $\deltat\to 0$. The limit is informative about
actions, namely, if a policy $\pi'$ satisfies $V^{\pi'}>V^{\pi}$ for all states, then
$A^\pi(s,\pi'(s))>0$ for some $s$.
\end{theorem}
}

@@

\TODO{
\begin{theorem}
Consider a near-continuous MDP in which an agent selects an
action according to an $\eps$-greedy policy that mixes a deterministic
exploitation policy $\pi$ with an action taken from a noise policy
$\pi^\text{noise}(a|s)$ with probability $\eps$ at each step. Then the
agent's trajectories converge when $\deltat\to 0$ to the solutions of the
\emph{deterministic} equation
\begin{equation}
d s_t/dt= (1-\eps) F(s_t,\pi(s_t))+\eps \E_{a\sim
\pi^\text{noise}(a|s)}F(s_t,a)
\end{equation}
\end{theorem}
}

@@

We learn $V_{\theta}$ and $A_{\psi}$ via suitable variants of $Q$-learning for continuous and
discrete action spaces. Namely, 
the true $A^\pi_\deltat$
and $V^\pi_\deltat$ of a near-continuous MDP with greedy exploitation
policy $\pi(s) \deq
\text{argmax}_{a'}A^\pi_\deltat(s, a')$
are the unique solution to the Bellman and consistency equations
\begin{align}
	V^{\pi}_\deltat(s) + \deltat\, A^{\pi}_\deltat(s, a) &=
	r\,\deltat + \gamma^{\deltat}  \,\E_{s'} V^{\pi}_\deltat(s')\label{eq:bellman_A}\\
	A^{\pi}_\deltat(s, \pi(s)) &= 0\label{eq:max_A}.
\end{align}
as seen in \ref{subsec:reparam}. Then $V_{\theta}$
and $A_{\psi}$ are trained to approximately solve these equations.
